\section*{Asus eeepc 1005HA and Meego 1.0.1}
\vskip 2pt

I bought my eeepc in last December and since then i am using Ubuntu Netbook Remix(UMR) or Ubuntu Netbook Edition(UNE). It was working good and with some hacks i was able to use it to the best.

I don’t use my netbook for much multimedia purposes(still i need to listen to a set of songs once in a while). I have a desktop from my institute and a another pc with a big screen TV connected to it for my multimedia choices. When i saw Meego coming out from maemo and moblin i was actually excited. There were many reason for excitement, one was of to see how they choose or combine the two legacies(maemo comes from so called debian side and moblin from fedora). Other was of happiness, since an os meant for mobile/smartphone computing will definitely be simple and faster.

Due to all excitement and my interest in OSes for netbooks based on Linux, i tried it out yesterday(yeah, i know its one and half months after 1.0 came out). To say the least, it was a very good system. Yeah there are a lot of drawbacks. But for a 1.0 release it appears pretty good.

The thing i hated most in the in these first 24 hrs is(whether you believe or not), it doesn’t have g++. It is quite essential to compile somethings which doesn’t come with the default system or in repository. Really speaking, i didn’t care that i don’t have multimedia capability, but g++ is essential for me.

As most of the other reviews say, interface is very good and the best for a netbook. I will go to the extent like, this is the best i have seen. Still there are issues with policy kit authetication(for my NTFS partition from windows installed by ASUS and ext4 of 10.04 UNE). Since the system or syslinux based bootloader doesn’t support ext4, i had to recover the grub for ubuntu(which took some of my time).

Lack of office programs wont bother me much, but i didn quite understand the part of gadget(which allows you to add numerous plugin scripts the system). Poorly designed and quite out of focus. I use latex and beamer for my document and presentation purposes, so i was ok when ooffice was not there in Meego. But, when i get a ODF standard document, i don’t really know what to do.

I noted another interesting aspect, the whole Meego claims to have Malayalam support and can input and render malayalam quite well(smc-fonts are missing, i am planning to put a repo in our savannah and later make sure meego uses smc-fonts and it comes default). Chromium has some issue when it comes to rendering Unicode 5.0(pre unicode 5.1 chilus, its not able to convert cons+virama+ zwj-> chillu). The interface renders it very well though. So, i think it has something to do with the chromium rendering modules(webkit i suppose, to be fair, chrome in windows doesn’t show such tendencies).

Anyway, for serious netbook users and for future smartphones, systems based on meego and android are the future. I am all out to make sure, malayalam is working perfect and out of the box for meego(its easier for me and since its built especially for atom, i am one of the few who can test it).

I will setup a repository for smc fonts for meego in savannah. Next step is to make meego developers add smc-fonts in the repo. Another task is about verifying the rendering issue with chromium(which might take time, since i need to find chromium users in GNU.Linux).

For a first release, i should say, meego is very impressive. Yeah i know it doesn’t have multimedia capabilities(can’t even play my MPs files), still it gets a lot of marks for the interface. If they succeed in making the interface flawless, with a good sync with policy-kit to authenticate, i think meego can make a big leap with next release.


\subsection*{Comments}
\begin{enumerate}
 \item{Ashik S}
 
I can help with testing things on Chromium – in fact Rajiv nair (mandoos) and me have it as our default browsers on our Ubuntu and Arch systems. GIve us the test cases and we will run them and give you the results.

 \item{jinsbond007}
 
hi,

Thanks.So far i have only one problem with chromium. Reading Malayalam.
I installed smc-fonts, Set the browser font to Meera and encoding to UTF8. But, it is having some issue with chillus formed by ZWJ.
I am going home tomorrow, so not sure when will i be able to give the details but i will try my best 

The problem is only with the browser, all apps are gtk based(but, there is qt also under the hood though no apps are yet available). Since MeeGo is a combination of Moblin and maemo, i think it will have these kind of behaviour 

 \item{行銷}
 
Hey can I copy and paste this post on my web site? What references must I give? You might give this info for other people too.

 \item{網路行銷}
 
The layout of the weblog is absolutely messed up when I look at it in Opera. Plz fix it.

 \item{Felicidad Heindl}
 
I do enjoy the way you have framed this specific situation and it does indeed supply me some fodder for consideration. Nevertheless, through just what I have seen, I only hope when the comments stack on that people keep on issue and not start upon a tirade involving the news du jour. Yet, thank you for this excellent point and although I can not really concur with the idea in totality, I respect the standpoint.

 \item{yogabis}
 
yogabis hello there and thank you for your information – I have definitely picked up something new from right here. I did however expertise several technical issues using this website, as I experienced to reload the site lots of times previous to I c…
hello there and thank you for your information – I have definitely picked up something new from right here. I did however expertise several technical issues using this website, as I experienced to reload the site lots of times previous to I could get i…

\end{enumerate}

\newpage 
