\secstar{Being Lonely (it is good if it makes you think!!!)}
\vskip 2pt
\begin{english}
For me being lonely is the time to think and let your mind gaze through the rich grasslands of life. Even when I am in a crowd, sometimes I will go thinking. I never need to be alone to feel alone. Being alone is simply something which happens to me anywhere unpredictable. When I feel like that, what I would do is to try and draw conclusions on what I have observed.

Once, on such an occasion, I was trying to draw conclusions on the truth of GOD. I just tried to think how GOD can be. As He is the One capable of driving the whole universe, He will be either somewhere outside the universe at a centralized place or a distributed source. The existence of such a centralized source is something which is beyond imagination and almost impossible when we think that it is having a role in each and everything happening in the whole universe (just think of a big energy source which provides the force for our movements within the Earth and for Earth to move around the sun and so on). It led me to the conclusion that the force can be something distributed every where in the whole universe (just understand that it is a simple conclusion by a crooked mind!!! I am ready to believe otherwise if you can convince me).

However, the problem still hadn't been solved completely. I just kept thinking what can that distributed source of power be. It should be something associated with each and everything. When I looked at it from such a perspective, it just occurred to me that whenever some chemical reaction happens, an amount of energy is released. All activities in the universe, when thought of, can be reduced simply to things which are using energy or things which displace energy. Energy is the single driving force in all the actions of the universe. All actions are exchanges or conversions of forms of energy!!!

Then I suddenly felt like, are things this simple? But when I started thinking deeply into the facts, it appeared clearer to me that, the concept of a single GOD or a group GODs or anything can be rounded off to the definition of it as the ultimate source of energy in the whole universe. Suddenly it appeared to me as something which explains everything (may be because it was so simple).

My thoughts then went into the fact that no religion or beliefs are explaining things like these. Then when I thought a little more, I understood that picturing God as something like a watchdog or The Ultimate Jury was a better solution to many problems in the society as well as answers to a bunch of questions (another one of my assumptions!!! Cross me if you want. Always welcome!!!).

This is just a sample of how my thoughts used to go when I am alone (not physically!!!). Please be patient to read more!!!

\subsection*{Comments}
\begin{enumerate}
\item{anwer: }
Great thought dude. The one I could identify very well was that of energy. If God is energy, then it can be classified as omnipotent or omnipresent. However, as you said, the humanity likes and most of them can only accept a God who is a jury and prosecutor. The God and spirituality in its present form has only lead the world to chaos and destruction. I believe that the knowledge about God should be expanded. ``All great new things were first called a blasphemy''. All great knowledge too. I recommend you to read the book ``\emph{Tomorrow's God} by \emph{Neale Donald}. Cheers!

\item{Navitha: }
Jinesh, well written. However, like all the things written in solitude, for these few lines that came from your thoughts, only you alone can interpret the depth of it completely. Yes, this question does come across everyone's mind regarding the existence and origin of God. Few just let it go by as a passing thought because once you start searching for an answer, it would go on from forever till eternity. Although the truth is that everyone do believe somewhere that there is some supernatural power that can change their lives no matter what!!! Otherwise people would not turn to God when nothing worldly can save them. Maybe it's the belief that has been fed into the human race since time immemorial.

However, unlike others, you gave it a thought. Liked some interesting interpretations of yours.
Let me quote you, ``I just kept thinking what can that distributed source of power be. It should be something associated with each and everything. When I looked at it from such a perspective, it just occurred to me that whenever some chemical reaction happens, an amount of energy is released.''. But didn't it occur to you what drove all these chemical reactions? There must be something that is causing such an action.

Well people have different concepts of what God is to them. Some feel that it is within them. Some feel its all over. Some worship them. Some bend down to him.
But to you it occurred that “Then when I thought a little more, I understood that picturing God as something like a watchdog”. If that was true, then how do you explain all the natural disasters? Where does the floods, volcanoes, Tsunamies and hurricanes stand? If he was such a watch dog would he ever do things to destroy his beautiful creations? Wouldn't he always maintain things in a ``picture perfect'' way so that nothing messes up with his possession?


\item{jinsbond007: }
Hi Navi,

May be my inabilities in expressing my thoughts at its best through writing made you think like that. As far as I know, nothing in this world happens as it is! It happens in an order, a pseudo random order! When I thought about this ordering, I found out that the action of energy behind these will explain this better than anything! I didn't write about that because, I thought people will be able to understand that I was thinking mere energy as the driving force behind everything!

cheers


\end{enumerate}
\end{english}
\newpage
