\secstar{Hospital Log 7}
\vskip 2pt
\begin{english}

It has been quite long since I wrote anything. The stay at hospital this time is not allowing me to have a lot of time to write and even note down my hospital experiences. To give the minimum details, I got admitted for my Bone Marrow Transplant on June 15th. On 16th, they put line, then shifted me to the Stem Cell Transplant Unit, an isolation ward for BMT patients. Then for 2 days, I got heavy chemotherapy and the next 3 days Total Body Irradiation. TBI was given in two sessions for 3 days. After that on 23rd, they transplanted or transfused the graft cells. So far so good. It was so for some more days, then effects of TBI started to show up. By the way, after chemo and TBI, I practically had no immunity system. To top it, I took kind of a risk with going for BMT with an unhealed chest infect (which is still there as residues). 

After transplant, food stopped, and it was all TPN or what was commonly called food packet and water and juices. Ailments started when chest infection shot up long before it was time for counts to come up. The situation became so bad that, I was shifted to the ICU. Doctors and nurses then said that it was just for observation to keep me calm. But understanding minds have a problem. They get what's going on around them without anyone telling them anything. Hidden conversations and random spurts of speech is enough for an observing and deducing mind to get the picture. 

Then the change started. From limited moving man from BMTU, I had be in full rest ICU patient in Isolation Unit. I was not able to inhale enough oxygen in to keep my self alive. Even with normal oxygen mask, they were giving me high pressure oxygen at 15 liters or so initially every two hours. It was kind of killing, a chilling 21 degrees and just one cotton gown over you with fever coming and going along with involuntary bowel and bladder movements. I took fights with each and everyone to kill my frustration, tried to find some comfort by praying. But sadly, it didn't help much. Then I decided it was better to show the right emotion. I cried, heart felt and cried. It worked a little better. Once the tears were over, things felt better. Rather than trying to adjust to the situation, I tried to fit myself into it. I had no idea how long it would take me to get out and how I will be when I get out. 

The toughest of the nights in the ICU was like that of any other new place, the first one. Though a bed was requested in the morning, by the time I got into isolation room in ICU it was evening 7. The room was kind of self sufficient and had lot of breathing machines, all of which they used to keep me alive. I am quite sure I was not the most co-operative patient they had. I threw out the high pressure oxygen mask when they connected it to such an effect that, the duty doctor got angry and shouted back at me. :) Since they don't use the Hiccmann's line, ICU people first put a line on my neck. Then later they found that it was making difficulties to flows while high pressure mask is connected. So they put one more line just above the thigh on my pelvis area. 
\end{english}
\newpage
