\secstar{Anivar's email to Swathanthra Malayalam Computing}
\enlargethispage*{3\baselineskip}
%{\vskip 2pt}
\begin{english}
Yes, I am writing this with tears. He was a close friend,
co-traveler, and colleague in SMC.

He was a student in IIIT Hyderabad, working on CVIT lab in the team
to develop a Malayalam OCR. He was under the treatment for Leukemia in
CMC Vellore for past 2 years. He was a very active contributor to
Swathanthra Malayalam Computing's projects and various other FOSS
projects such as pypdflib, Silpa project, etc. even from his hospital
bed. In addition he used to write articles in malayal.am on various
topics. In FEC also he was quite active and contributed to various
discussion threads. He was one among SMC's  Google Summer of Code
candidates in 2007. His contribution to standardization discussions
such as critique to International Domain Names Standard for Malayalam,
Inscript 2 Draft Keyboard Standard, etc. was also commendable.

He was always available on Google chat when he is in the intervals
between treatments. We used to talk a lot about various contemporary
topics. Jinesh was working on a paper about pitfalls in Biometric
standards UID adopted, and he used to send a lot of contemporary
research papers on biometrics to me.

Our last chat (around September 4th) was about planning get together, when
he reaches home after treatments.
Whenever we ask about his treatment details he used to show this XKCD comic
\url{http://xkcd.com/931/}

When he was in MES, he was the organiser of many FOSS activities in
their campus and he was an initiator for Swatantra software user group
Malappuram.
\end{english}

\subsection*{ജിനേഷിന്റെ മറ്റ് സൈബര്‍ സാന്നിദ്ധ്യങ്ങള്‍}
Blog \url{http://www.jinsbond.in/} \\
Facebook \url{https://www.facebook.com/jinesh.jayaraman} \\
Twitter \url{http://twitter.com/#!/jinsbond007} \\
Picasa \url{http://picasaweb.Google.com/jinesh.k} \\
\url{http://fci.wikia.com/wiki/User:Jinesh.k} \\
\url{https://github.com/santhoshtr/pypdflib/commits/master} \\
\url{http://code.Google.com/p/tesseractindic/wiki/IndicLanguageTesseract}
\newpage
