\begin{english}
\secstar{My notes on Jinesh}

Jinesh, I never met him personally nor I knew who he was. He used to
send patches once in a while to the SILPA project. I actually came close
to the guy when I started seeing the commits from him on pypdflib
project. Even though I was doing periodic commits to pydpflib, my
commits were basically just back ground fixes and optimizations rather than
actual code for pydpflib core functionality. We did find a few issues
and logged them in savannah project page. \footnote{\url{http://savannah.nongnu.org/bugs/?group=pypdflib}} Jinesh started to
commit on these issues, fixing them one by one. He used to come online
and discuss things with me and we used to have very long elaborated
discussions. I still didn't know what Jinesh was doing. It was then
Santhosh told me that Jinesh was in Hospital fighting Blood Cancer and
I was shocked to hear that. Because when you talk with him you really
can't make out that the guy is coding things and chatting from his hospital bed,
fighting one of the deadliest diseases known to mankind. Well, I didn't
interact much with him after that. Probably because he was undergoing
more medical therapies and was not getting time to come online.

After a month or two, I got the shocking news from Santhosh that Jinesh
was no more! I did not have words to express my grief. Moreover, if you see the pypdflib
commit logs, you will see that the last commits were made by Jinesh and after
him, the project almost went to an inactive state. There are a couple of
tasks which was assigned to me by Jinesh which I think I never
completed.\footnote{\url{http://savannah.nongnu.org/task/?group=pypdflib}}

In short words we lost a great contributor and a good friend. Even
though we never met, he was a really nice and cheerful person. I will
miss him.

Vasudev Kamath, Contributor - various indic language computing projects
 \end{english}
 \newpage
