\begin{english}
\secstar{Account of a campus gang war!!!}
\vskip 2pt
This is an account of a mob in a well known self financing engineering college, from the words of students of the college. It is from MES College of Engineering, and most newspaper reports are not taking into account what the root cause of the problem is. I just tried to interact with some of my juniors there and got these details. This account is written on the basis of a chat conversation, which is published here. Some details I confirmed and crosschecked, basically those regarding the program at the auditorium and all. I just want to point out how a ordinary gang or group fight at college turned out to be a political (?) issue. I never call this as student politics, but student gang war.

There are more than enough issues at college, and without fighting for those, these student politicians (?) are fighting for head counts. I don’t know what leads these students. Anyway, I believe it is not the professionalism that all are expecting from young engineers.

On Friday, the 23\textsuperscript{rd} of November 2007, there was a screening for some program (guess its name was Dyuthi 07) going on in the auditorium. It was going well until the Mechanical fellows started shouting ROYAL MECH, to which the the EEEs responded by shouting CHOPPERS. The people present there said that they saw many chairs flying around. The situation was brought under control by the police.

Later, on Sunday (25\textsuperscript{th} November) morning (night), at about 1:30 AM, while everyone were asleep, a few locals came to the hostel and destroyed an inmate’s computer. Another inmate who rushed to the scene on hearing the noise was brutally attacked with weapons like chains, iron rods and haxo blade. He suffered injuries to his head, arm and foot.
A big strike was planned for Monday (26\textsuperscript{th} November) by KSU-MSF. The SFI-DYFI were also on strike and had lot of local support with them. Police rushed to the scene in large numbers. There were 3 jeeps and 2 vans full of police with their new ‘laathi’s. The strike was peaceful. Classes were suspended for the day.

The locals found some tools (iron rods) on the road and reported to the police. They said more would be found at the hostel and asked the police to raid the place. Some locals came along as well. However, the students weren't happy at this. Pushing and pulling took place which was followed by throwing of stones. The police stopped the raid and came to the middle and used laathi to separate the two groups. Some were injured.
Along with the students and the people, a news reporter was also injured. The bikes of two students were also destroyed by the DYFI activists.

The final outcome was, the college was closed for a week. The first internal exam, which was scheduled to be conducted in the first part of the old semester, was again postponed. Also many students were injured and hospitalized. I was seeing this game of settling scores for a long time, and now just a problem in a cultural show turned out to be a big issue (settling accounts!). I don’t know who is benefiting from these gang wars.

(Also heard some students were harassed while going home after all these. Didn't get the details though. Will put up those details too as soon as possible.)

\begin{flushright}(November 27, 2007)\end{flushright}
\end{english}
\newpage
