\secstar{Please Read the Offer Document Carefully Before...}
\vskip 2pt

{\engtext
I hope all are familiar with the above words. After all those Shining India mutual fund advertisements, a warning like this is mandatory. I felt the same regarding the offer documents supplied at campus placements after reading a news in economic times about the act of Keane India on last Monday. A small account of it can be read over here\footnote{\url{http://www.itexaminer.com/Outsourcing/tabid/77/articleType/ArticleView/articleId/794/Keane-chops-400-staff.aspx}}.

I can imagine a little about what was there within the minds of those people who got sacked. I believe all of them were people who got placements through campuses (since Keane takes 80\% of their workforce from campus and it is not easy to send one with prior experience). All the offer documents I got (not many anyway. Only two) had one section called "Job Termination". There was a notice period specified before terminating the job. It usually varies according to your value and employers value. For me those values were in months.

Friends who get a job from campuses usually do not bother to read through the whole document before agreeing and sending it to the specified address. Or even if they did take time to read, thinking about loosing the job, nobody would be ready to reject any job they have in hand. Moreover, the monetary benefits page blinds them while reading through other instructions. I rejected a job in industry for one in research in academia. As the academia is not as rich as corporate India and my preference was not monetary, the one I rejected was the one which gave me more monetary benefits. That made me answer a lot of questions like, ``how much do you think you will get after you complete the course'', ``Is that bigger than what you will get after that time in industry'' and a lot of other similar questions. People who are not ready to ignore the curiosity of people also don’t like to reject some offer despite of the risk associated with it.

But they are not understanding that, the value of people who gets fired by a company for which they spend two years is not impressive unless you have made a value for your own. The companies which favour new recruits than experienced professionals, sometimes take around 2 to 3 weeks to give the offer document after placing a verbal offer. The figures they boasted at the recruitment drive might never match, or appears like only something which you get after the highest performance incentive and no tax cuts. 

Friends, money matters. But it is not the only thing that matters. The first job is your life and so you'd better be careful with it. Please read the full document, even the fine prints. In case of any doubt, call the company or mail them. Usually they provide an explanation. Placement offices in colleges, more than making the numbers, please teach your students about the importance of a job and how one should be careful about offer documents. Moreover, students, even when you are doing a job, try to make your own space in the world so that even at the worst moment of the company, firing you should be their last option!

"So please read the offer document carefully before investing your life"

(June 19, 2008)
}
\newpage
